(tentative) Rotational Spectral Unmixing of Exoplanets

### 2016-10-18 paper/main.tex
text updated, figure trimmed
text and figures updated
merged
forgot to commit

\author{
%
Yuka Fujii\altaffilmark{1,2} 
%
Jacob Lustig-Yaeger\altaffilmark{3} 
%
Nicolas Cowan ?\altaffilmark{4} 
%
}

@@

\memoYF{\citet{Cowan2013} found a more reasonable answer for $s$ when they fitted with $\{ f, s \}$, but I think this is a coincidence. }

@@

The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
Such assumption can be represented by the prior of 
%%%
\begin{equation}
\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
\end{equation}
%%%
or
%%%
\begin{equation}
\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
\end{equation}
%%%
where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
In this paper, we assume squared exponential covariance function, i.e., 
%%%
\begin{equation}
\tilde \Sigma _{ii'} = \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
\end{equation}
%%%
where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
%%%
\begin{equation}
\Sigma _{ll'} = \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
\end{equation}
%%%
where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hb!]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
    \end{center}
     \end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
    \end{center}
\end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
    \end{center}
 \end{minipage}
   \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
    \end{center}
 \end{minipage}
    \caption{Our mock data based on Earth surface. }
\label{fig:mockdata}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!bpth]
    \begin{center}
\includegraphics[width=\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal Components. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!bpth]
    \begin{center}
%\includegraphics[width=\hsize]{PCA_projected.pdf}
\includegraphics[width=\hsize]{mockdata_quadrature_PCplane_reduced.pdf}
    \end{center}
    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_time.pdf}
\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
    \end{center}
    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!tb]
    \begin{center}
\includegraphics[width=\hsize]{EPOXI_vislightcurve_4obs.pdf}
    \end{center}
    \caption{4 light curves of the Earth obtained with EPOXI mission.}
\label{fig:EPOXIlc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Retrieval using equation (\ref{eq:}) }
\label{ss:retrieval}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

First, each series of data is analyzed separately. 
Without regularization and with regularization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{s:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Uncertainty in Radius}
\label{ss:radius}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity to Initial Condition}
\label{ss:initialcondition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{s:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\author{
%
Yuka Fujii\altaffilmark{1,2} 
%
Jacob Lustig-Yaeger\altaffilmark{3} 
%
Nicolas Cowan\altaffilmark{4} 
%
}

@@

@@

The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
Such assumption can be represented by the prior of 
%%%
\begin{equation}
\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
\end{equation}
%%%
or
%%%
\begin{equation}
\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
\end{equation}
%%%
where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
In this paper, we assume squared exponential covariance function, i.e., 
%%%
\begin{equation}
\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
\end{equation}
%%%
where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
%%%
\begin{equation}
\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
\end{equation}
%%%
where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bth!]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
    \end{center}
     \end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
    \end{center}
\end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
    \end{center}
 \end{minipage}
   \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
    \end{center}
 \end{minipage}
    \caption{Our mock data based on Earth surface. }
\label{fig:mockdata}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[th]
    \begin{center}
\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal Components. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{center}
%\includegraphics[width=\hsize]{PCA_projected.pdf}
\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
    \end{center}
    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_regtime_l1e-2.pdf}
    \end{center}
    \caption{Result of estimation for $\{ \fast,\,s\}$ with $\lambda = 0.01$. \memoYF{MC chains do not fully converge in 5000 steps. The evolution of the chains are very weird.}}
    \label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_regtime_l1e-4.pdf}
    \end{center}
    \caption{Result of estimation for $\{ \fast,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
    \end{center}
    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.01$. \memoYF{MC chains do not fully converge in 5000 steps, and it is not a single peak!!}}
\label{fig:xmed_std_reglong_l1e-2}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
    \end{center}
    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
%    \end{center}
%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_time.pdf}
%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
%    \end{center}
%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\appendix

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b!]
    \begin{center}
\includegraphics[width=\hsize]{EPOXI_vislightcurve_4obs.pdf}
    \end{center}
    \caption{4 light curves of the Earth obtained with EPOXI mission.}
\label{fig:EPOXIlc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
